---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swecris

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/KTH-Library/swecris/workflows/R-CMD-check/badge.svg)](https://github.com/KTH-Library/swecris/actions)
<!-- badges: end -->

The goal of the `swecris` R package is to provide access to data from SweCRIS, a national database that allows you to see how participating research funding bodies has distributed their money to Swedish recipients. SweCRIS is managed by the Swedish Research Council on behalf of the Government. This R package uses the open API at SweCRIS to make data available for use from R.

## Installation

You can install the development version of `swecris` from [GitHub](https://github.com/KTH-Library/swecris) with:

``` r
library(devtools)
install_github("swecris", dependencies = TRUE)
```

## Example

This is a basic example which shows you how to get data about projects at KTH Royal Institute of Technology:

```{r example, message=FALSE}
library(swecris)
suppressPackageStartupMessages(library(dplyr))

# either fetch the data from the API
#kth_projects <- swecris_funding()

# or use the bundled data
kthf <- swecris_kth

# top ten largest fundings containing abstracts with the word "data"
library(dplyr)

fundings <- 
  kthf %>%
  mutate(total_funding = as.numeric(FundingsSek)) %>%
  arrange(desc(total_funding)) %>%
  filter(grepl("data", ProjectAbstractEn)) %>%
  slice(10)

# display an example record
fundings %>%
  glimpse()

```

Given an organisation, get information about projects:

```{r}

orgid <- 
  swecris_organisations() %>%
  filter(grepl("^KTH, ", organisationNameSv)) %>%
  dplyr::pull(organisationId)

kthp <- swecris_projects(orgid)

# ten upcoming projects
projects <- 
  kthp %>% arrange(desc(lubridate::ymd(fundingStartDate))) %>% 
  select(-starts_with("projectAbstract")) %>%
  select(
    projectId, 
    projectTitleEn, 
    projectStartDate, 
    projectEndDate, 
    fundingOrganisationNameEn, 
    fundingsSek, 
    fundingYear
  ) %>%
  head(10)

knitr::kable(projects)
```

Swedish list for 2021 (the first few records):

```{r}
sl <- 
  swecris_list_swedish()

glimpse(sl %>% head() %>% collect())

knitr::kable(sl %>% head() %>% collect())
```

Some other Nordic list referenced at SweCRIS are also provided:

```{r}
f <- swecris_list_finnish()
n <- swecris_list_norwegian
d <- swecris_list_danish()

glimpze <- function(df) {
  df %>% head() %>% knitr::kable()
}

glimpze(f)
glimpze(n)
glimpze(d)
```
