---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swecris

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/KTH-Library/swecris/workflows/R-CMD-check/badge.svg)](https://github.com/KTH-Library/swecris/actions)
<!-- badges: end -->

The goal of the `swecris` R package is to provide access to data from SweCRIS, a national database that allows you to see how participating research funding bodies has distributed their money to Swedish recipients. SweCRIS is managed by the Swedish Research Council on behalf of the Government. This R package uses the open API at SweCRIS to make data available for use from R.

## Installation

You can install the development version of `swecris` from [GitHub](https://github.com/KTH-Library/swecris) with:

``` r
library(devtools)
install_github("swecris", dependencies = TRUE)
```

## Example

This is a basic example which shows you how to get data about projects at KTH Royal Institute of Technology:

```{r example, message=FALSE}
library(swecris)
suppressPackageStartupMessages(library(dplyr))

kth_projects <- 
  swecris_search()

# display one of the search hits

project <- 
  kth_projects$hits %>%
  mutate(total_funding = as.numeric(total_funding)) %>%
  arrange(desc(total_funding)) %>%
  filter(grepl("data", abstract_en)) %>%
  slice(2)

project %>%
  glimpse()

```

Given a project identifier, one can retrieve information about a specific project:

```{r}
p1 <- swecris_project("2019-05221_Vinnova")

# its funding organization
p1$documentList$documents$organizations$funding[[1]]$en

# and various other details
p1$documentList$documents$dates

# such as its project leader
swecris_project_leaders("2019-05221_Vinnova")
```

